\documentclass[letterpaper,12pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}

%add portfolio website in project

\begin{document}

\linespread{1}\selectfont
\setlist[itemize]{left=0pt, itemsep=-5pt, topsep=0pt, after=\vspace{0pt}, label=\tiny\textbullet}
\newcommand{\sectionrule}[1]{
  \vspace{5pt}
  \RaggedRight
  {\large\textnormal{#1}}
  \hrule
  \vspace{3pt}
}
\pagestyle{empty}

\begin{center}
    \textbf{\Large Soobin Yang}\\
    \faPhone { 330-990-4796}
    \faEnvelope \href{mailto:yasoo8449@gmail.com}{ yasoo8449@gmail.com} \hspace{1pt}
    \faGithubSquare \href{https://github.com/uliba3}{ github.com/uliba3} \hspace{1pt}
    \faLinkedinSquare \href{https://linkedin.com/in/soobin84}{ linkedin.com/in/soobin84}
\end{center}

\vspace{-10pt}

\sectionrule{Education}
\textbf{B.A. in Computer Science and Math}\textnormal{, The College of Wooster - 3.9 GPA} \hfill \textnormal{Aug 2022 - May 2025}\\

\sectionrule{Experience}
\textbf{Software Developer Intern}\textnormal{, Omniscience Strategies - San Jose, CA} \hfill \textnormal{May 2024 - present}\\
\begin{itemize}
    \item Developed a demo product through the full agile software development life cycle. Contributed to frontend, backend, infra, and DevOps tasks using JavaScript, Python, SQL, Docker, Terraform, and Bash.
    %\item Developed a Chrome extension version of the product, wrote 50\% of the code. Integrated Firebase authentication login by copying firebase library directly and enabling a chat feature using REST API.
    \item Integrated login and chat feature in chrome extension version of the product by utilizing REST API and Firebase authentication. Avoiding pulling external libraries to follow manifest v3's policy.
    \item Added multi user support by data isolation using multi-tenancy in Weaviate to increase the security, migrating 5000+ data entries in single-tenant to multi-tenant database with 0\% data loss.
    \item Automated AWS deployment using Terraform and Docker, reduced deployment time by 30\%. Enhanced security by making server connections private and retrieving keys from AWS Secret.
    \item Designed a testing pipeline that runs when code is pushed, made 50+ test cases and boosted test coverage by 20\%. Created server status monitoring shell script, covering 80\% of the API endpoints.
\end{itemize}

\textbf{Web Designer}\textnormal{, The College of Wooster - Wooster, OH} \hfill \textnormal{Apr 2024}\\
\begin{itemize}
    \item Refactored \href{https://mmproject-three.vercel.app/}{the college's photography website} using HTML, CSS, and JavaScript. Developed photo categorization feature for managing 150+ photos, and improved UI/UX based on user feedback.
    \item Optimized performance with lazy loading and code splitting, reducing page load time by 40\%.
\end{itemize}

\textbf{CS Research Assistant}\textnormal{, The College of Wooster - Remote} \hfill \textnormal{Jan - May 2024}\\
\begin{itemize}
    \item Documented 30+ papers on increasing the performance of large language models in tabular data.
    \item Found methods from existing research to improve accuracy by 20\% using RAG and CoT technique.
\end{itemize}

\sectionrule{Activities}
\textbf{Competitive Programming}
\textit{C++}
\begin{itemize}
    \item Coded efficient data structures, algorithms, and math solutions to solve problems in competition.
    \item 18th/500 in PC Koushien Qualifiers 2020 (UoAizu) as a team of duo, 4th/20 in SuperCon 2021 (Tokyo Tech) as a team of triple, 4th/20 in Denison Programming Contest 2024 as a team of quad.
    %\item Placed 18th of 500 teams in 2020 PC Koushien Qualifiers at Aizu University, competing as a duo.
    %\item Placed 4th of 20 teams in SuperCon 2021 held by Tokyo Tech University, competing as a trio.
    %\item Placed 4th of 20 teams in Denison Programming Contest 2024, competing as a quad.
\end{itemize}

\textbf{Fun Hackathon 2024}
\href{https://echodelphi.github.io/}{\faGlobe}
\href{https://github.com/echodelphi/echodelphi.github.io}{\faGithub}
\textit{TypeScript, React}
\begin{itemize}
    \item Placed 2nd of 8 teams in Fun Hackathon 2024 held by Hacker Dojo. Started from finding 5 teammates, ideating, designing, coding, and presenting to the 50+ audience in 2 days.
    \item Made a frontend website to summarize live audio transcription real time using deepgram and llm API.
    \item Coded llm integration part and articulated the technical stack for 1 minute during the presentation.
\end{itemize}

\sectionrule{Projects}
\textbf{Full-stack BookStore web application}
\href{https://bookstore-backend.fly.dev/}{\faGlobe}
\href{https://github.com/uliba3/BookStore-backend}{\faGithub}
\textit{React, Express.js, Node.js, MongoDB, Bootstrap}
\begin{itemize}
    \item Full-stack web application to log in, search, and save 40+ million books from Google Books API.
    \item Erased 70\% redundant api calls by saving book's data to user's table and login token in local storage.
\end{itemize}

\textbf{X (Twitter) News Summarization bot}
\href{https://x.com/NewsWorldJapan}{\faGlobe}
\href{https://github.com/uliba3/News_World_Japan_X_bot}{\faGithub}
\textit{Python, Docker, GitHub Actions}
\begin{itemize}
    \item Bot with 50k+ post views, translates summarized english news by GitHub Actions' CI/CD pipeline.
    \item Reduce pipeline run time by 3 minutes using docker and read keys from repository secrets for security.
    \item Web scrape contents in BeautifulSoup and summarize the content to 200 characters using gemini api.
\end{itemize}

\textbf{AI Web Chatbot Chrome Extension}
\href{https://chromewebstore.google.com/detail/eeckhenackiojmofodkcoogkkfggkkap}{\faGlobe}
\href{https://github.com/uliba3/ai-web-chatbot}{\faGithub}
\textit{HTML, CSS, JavaScript}
\begin{itemize}
    \item Chrome extension with active users, can ask AI about the current web page using gemini API.
    \item Saves API key in chrome storage, parse HTML into text and make API request of up to 700k+ words.
    \item Makes movable and resizable chatbox by event listeners and DOM manipulation with 20ms latency.
\end{itemize}

\sectionrule{Skills}
\textbf{Frontend:} \textnormal{HTML, CSS, Bootstrap, JavaScript, React}\\
\textbf{Backend:} \textnormal{Node.js, Express.js, FastAPI, SQL, MongoDB, Weaviate}\\
\textbf{Tools/Other:} \textnormal{C++, Python, Git, Terraform, Docker, AWS, Firebase, Bash}\\
\end{document}