\documentclass[a4paper,12pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.25in, bottom=0.25in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}

%put it in chatgpt and personalize it for the job

\begin{document}

\linespread{1}\selectfont
\setlist[itemize]{left=0pt, itemsep=-5pt, topsep=0pt, after=\vspace{0pt}, label=\tiny\textbullet}
\newcommand{\sectionrule}[1]{
  \vspace{-15pt}
  \section*{\normalfont #1}
  \vspace{-10pt}
  \hrule
  \vspace{5pt}
}
\pagestyle{empty}

\begin{center}
    \textbf{\LARGE Soobin Yang}
    \hrule
    \vspace{5pt}
    \faEnvelope \hspace{1pt} \href{mailto:yasoo8449@gmail.com}{yasoo8449@gmail.com} \hspace{5pt}
    \faGithubSquare \hspace{1pt} \href{https://github.com/uliba3}{github.com/uliba3} \hspace{5pt}
    \faLinkedinSquare \hspace{1pt} \href{https://linkedin.com/in/soobinyang8449}{linkedin.com/in/soobinyang8449} \\
    \faGlobe \hspace{1pt} \href{https://uliba3.github.io/portfolio/}{uliba3.github.io/portfolio}
\end{center}

\vspace{-20pt}

\sectionrule{Education}
\textbf{\large The College of Wooster} \hfill \textnormal{Aug 2022 - May 2025}\\
\textit{B.A. in Computer Science and Mathematics, Dean's List, GPA: 4.0}
\begin{itemize}
    \item \textbf{Computer Science courses:} Data Structures and Algorithms, Database Systems, Computer Networking and Communication, Algorithm Analysis, Theory of Computation
    \item \textbf{Mathematics courses:} Linear Algebra, Transition to Adv Mathematics, Multivariate Calculus, Probability Theory, Statistical Theory, Applied Statistics
\end{itemize}

\sectionrule{Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} C++, Python, JavaScript, R
    \item \textbf{Web Development:} HTML, CSS, Bootstrap, React.js, Node.js, MongoDB
    \item \textbf{Other Skills:} LaTeX, UNIX, Git, Korean, Japanese, English
\end{itemize}

\sectionrule{Experiences}
\textbf{\large AI Solutions Intern} \hfill \textnormal{Jan 2024 - present}\\
\textit{Matsuo Institute} \hfill \textit{Remote}
\begin{itemize}
    \item Developed AI solutions for a new business project in Fortune 1000 global company.
    \item Conducted research, interviews, and surveys for informed business development.
    \item Utilized LLM and ChatGPT API for prototype generation.
    \item Contributed to MVP development and conducted PoC.
    \item Presented data analysis and value propositions in client interactions.
\end{itemize}
\textbf{\large Research Assistant} \hfill \textnormal{Jan 2024 - present}\\
\textit{The college of Wooster} \hfill \textit{Wooster, OH}
\begin{itemize}
    \item Conducted research in the field of perturbation theory within mathematics
    \item Reviewed and evaluated research papers relevant to probabilistic and stochastic phenomena.
    \item Computed perturbations of various mathematical objects.
    \item Explored deep reinforcement learning (DRL) as an effective approach in Stock Prediction Using Event-based Sentiment Analysis.
    \item Researched machine learning papers and implemented models using Python.
\end{itemize}

\sectionrule{Projects}
\textbf{Browser-based Circle Game}
\href{https://uliba3.github.io/CircleGame/}{\faGlobe}
\href{https://github.com/uliba3/CircleGame}{\faGithub}
\textit{HTML, CSS, JavaScript}
\begin{itemize}
    \item Casual game to place and grow circles while avoiding collisions with the canvas edges or other circles.
    \item Utilized event listeners for keyboard and mouse inputs to control game interactions.
    \item Used localStroage to persist the highest score across sessions.
\end{itemize}
\textbf{Task Manager}
\href{https://uliba3.github.io/TaskManager/}{\faGlobe}
\href{https://github.com/uliba3/TaskManager}{\faGithub}
\textit{React}
\begin{itemize}
    \item A web-based task management tool to add, edit, delete, and sort tasks.
    \item Used redux and localStorage to manage and store tasks saved.
\end{itemize}
\textbf{Full-stack QA webapp}
\href{https://white-voice-4708.fly.dev/}{\faGlobe}
\href{https://github.com/uliba3/Q-A-backend}{\faGithub}
\textit{React, Node.js, MongoDB, Fly.io}
\begin{itemize}
    \item Enables users to post and see answers to random questions saved using MongoDB.
    \item Implemented a RESTful API using Node.js and Express.js to handle HTTP requests and responses.
\end{itemize}
\textbf{Full-stack BookStore webapp}
\href{https://bookstore-backend.fly.dev/}{\faGlobe}
\href{https://github.com/uliba3/BookStore-backend}{\faGithub}
\textit{React, Node.js, MongoDB, Bootstrap, Fly.io, Google Books API}
\begin{itemize}
    \item Users can explore and save books using the Google Books API, with data stored in MongoDB.
    \item Employed the bcrypt library to encrypt passwords, ensuring robust security measures.
    \item Implemented a RESTful API using Node.js and Express.js to handle HTTP requests and responses.
    \item Utilized Bootstrap to implement a modern interface, enhancing the overall design and user experience.
\end{itemize}

\sectionrule{Activities}
\textbf{Competitive Programming} \hfill \textnormal{Aug 2020 - present}
\begin{itemize}
    \item 4th in Supercomputing Contest 2021(by Tokyo Tech), 18th in PC koushien Qualifiers 2020(by UoAizu)
\end{itemize}

\end{document}
